Red Oak: Something Something Algorithmic Policy

### 2015-05-06 draft.tex
..

\begin{figure}[ht]
  \begin{lstlisting}
(* abstract packet type *)
type packet

(* a standard packet field *)
type field = IpSrc | IpDst

(* range is a union of intervals *)
type range = (int*int) list

(* minimum, maximum value for a range interval *)
val min_value: int 
val max_value: int

(* forwarding decision can deliver, drop, forward, multicast *)
type forwarding_decision =
	| Deliver
	| Drop
	| ForwardTo of int
	| Multicast of forwarding_decision * forwarding_decision
	| Ctrl (* TODO: should not expose this *)

(* in_range p f r returns true if the value of field f of packet p is in range r, and false otherwise *)
val in_range: packet -> field -> range -> bool
\end{lstlisting}

@@

\begin{figure}[ht]
  \begin{lstlisting}
(* name of a relation *)
type relation = string

(* add packet's fields to a relation *)
val add: packet -> field list -> relation -> unit

(* remove packet's fields from a relation *)
val remove: packet -> field list -> relation -> unit

(* test if a packet's fields are in a relation *)
val in_relation: packet -> field list -> relation -> bool
\end{lstlisting}

@@

\begin{figure}[ht]
\begin{lstlisting}
let compile (f: packet -> forwarding_decision) : policy =
      push most general packet to (empty) stack
      set the current location to be the root of an empty decision tree
      while (stack is not empty)
         pop the top of the stack as pkt
         run f of pkt resulting in a forwarding decision fd (and a modified packet pkt)
         record the forwarding decision for the symbolic packet pkt at the current location in the decision tree
         set the current location to be the root of the decision tree and repeat

\end{lstlisting}
\caption{Pseudocode for the compile function}
\label{fig:compile-pseudo}
\end{figure}

@@

\begin{figure}[ht]
\begin{lstlisting}
let run (pol: policy) (inputs: ((field*int) list) list) : unit =
      build the symbolic rules for policy pol
      generate the concrete rules with all relations empty
      for each packets in input,
          find the first of the current rule matching the packet, and record the forwarding decision fd
          if packet is sent to the controller then
              evaluate the policy on the packet, potentially adding or removing tuples from relations, record forwarding decision fd'
              regenerate concrete rules
              forward the packet according the forwarding decision fd'
          else
              forward the packet according to fd 
\end{lstlisting}

\caption{Pseudocode for the run function}
\label{fig:run-pseudo}
  \end{figure}

>>>>

\begin{figure}[ht]
  \begin{lstlisting}
type packet

type field = IpSrc | IpDst

type range = (int*int) list

val min_value: int 
val max_value: int

type forwarding_decision =
	| Deliver
	| Drop
	| ForwardTo of int
	| Multicast of forwarding_decision * forwarding_decision
	| Ctrl

val in_range: packet -> field -> range -> bool
\end{lstlisting}

@@

\begin{figure}[ht]
  \begin{lstlisting}
type relation = string

val add: packet -> field list -> relation -> unit

val remove: packet -> field list -> relation -> unit

val in_relation: packet -> field list -> relation -> bool
\end{lstlisting}

@@

\begin{figure*}[ht]
\begin{lstlisting}
let compile (f: packet -> forwarding_decision) : policy =
      push most general packet to (empty) stack
      set the current location to be the root of an empty decision tree
      while (stack is not empty)
         pop the top of the stack as pkt
         run f of pkt resulting in a forwarding decision fd (and a modified packet pkt)
         record the forwarding decision for the symbolic packet pkt at the current location in the decision tree
         set the current location to be the root of the decision tree and repeat

\end{lstlisting}
\caption{Pseudocode for the compile function}
\label{fig:compile-pseudo}
\end{figure*}

@@

\begin{figure*}[ht]
\begin{lstlisting}
let run (pol: policy) (inputs: ((field*int) list) list) : unit =
      build the symbolic rules for policy pol
      generate the concrete rules with all relations empty
      for each packets in input,
          find the first of the current rule matching the packet, and record the forwarding decision fd
          if packet is sent to the controller then
              evaluate the policy on the packet, potentially adding or removing tuples from relations, record forwarding decision fd'
              regenerate concrete rules
              forward the packet according the forwarding decision fd'
          else
              forward the packet according to fd 
\end{lstlisting}

\caption{Pseudocode for the run function}
\label{fig:run-pseudo}
  \end{figure*}
